### 2020-07-16 scache/jpdc/tex/impl.tex
*: update

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task are modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCache records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, \edited{which is defined by the memory usage,} the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

{\color{black}
\subsection{Discussion of Fault Tolerance}\label{fault}
% how to handle faults? -> maybe replication -> tradeoff
\edited{Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once),}
% For now, 
SCache only restarts failed workers without recovering their data \edited{and} leaves the fault handling to the DAG frameworks.
If a failure happens in a SCache worker during shuffle phases, the \edited{\texttt{getBlock}} API will return a \edited{data-not-found} error which causes the DAG framework restarts the current stage.
During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.

\edited{Although the entire computing task has to be re-computed, we consider that there is a trade-off between the efficiency and the overhead of fault recovery with SCache.}
A possible way to avoid this re-computing is to use replications to recover the data.
However, such replications can introduce a significant network overhead.
We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

>>>>

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task are modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCache records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, \edited{which is defined by the memory usage,} the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
\reedited{The lower the threshold is set, the more shuffle requests are issued since the amount of data to be shuffled remains the same.}
After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

{\color{black}
\subsection{Discussion of Fault Tolerance}\label{fault}

\reedited{For fault tolerance,} SCache only restarts failed workers without recovering their data.
If a failure happens in a SCache worker during shuffle phases, \reedited{SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing}.
During the re-computing, \reedited{the DAG frameworks can still use SCache to gain benefits in the shuffle phase.}

\edited{Although the entire computing task has to be re-computed, we consider that there is a trade-off between the efficiency and the overhead of fault recovery with SCache.}
\reedited{SCache brings significant performance benefits due to the in-memory shuffle management, although the overhead such as re-computing is also introduced when failure occurs, we believe such drawback is tolerable.
A possible soltion to avoid re-computing is to use replicas to recover the data.
However, such a strategy can introduce significant network overhead.}
% However, such replications can introduce a significant network overhead.

\reedited{Moreover, in the current design of SCache, we leave the server faults (e.g., node failures) to the DAG frameworks, due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once).}
We believe \reedited{this} way is more promising \reedited{since} most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark.
% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
}

### 2020-07-16 scache/jpdc/tex/optimization.tex
update
*: update

To solve this problem, we propose a new methodology named \textit{weighted reservoir sampling}.
SCache uses this method instead of the linear regression to predict output when using a RangePartitioner or a customized non-hash partitioner.
% we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
% Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data. 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
The $inputSize_j$ is the input size of $j$th map task. 
% Note that sampling does not consume the input data of map tasks. 
% The $BlockSize_{ji}$ can be calculated by:
$BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide a much more accurate result than the linear regression. 
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}

@@

\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in \edited{decreasing} order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx+1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor\newline
		\Return $M$
	\EndProcedure
	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.\newline
		% \State Return if it is impossible.
		\Return
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

@@

\begin{minipage}{0.95\columnwidth}
	\begin{algorithm}[H]
	\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
	\label{mhminheap}
		\begin{algorithmic}[1]
		\small
		\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\textit{shuffles}}$}
			\State $m\gets$ partition number of map tasks
			\Comment \textit{shuffles} are the previous schedule result 
			\ForAll{$r$ in $p\_reduces$}
				\State $r.size \mathrel{+}= \text{\textit{shuffles}}\left[r.rid\right].size$
				\State $new\_prob\gets \text{\textit{shuffles}}\left[r.rid\right].size / r.size$
				\If{$new\_prob\geq r.prob$}
					\State $r.prob\gets new\_prob$
					\State $r.host\_id\gets \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$
				\EndIf
			\EndFor
			\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
			\ForAll{$host\_id$ in $M$}
				\Comment Re-shuffle
				\ForAll{$r$ in $M\left[host\_id\right].reduces$}
					\If{$host\neq \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$}
					\State Re-shuffle data to $host$
					\State $\text{\textit{shuffles}}\left[r.rid\right].assigned\_host\gets host$
					\EndIf
				\EndFor
			\EndFor
			\Return $M$
		\EndProcedure
		\end{algorithmic}
	\end{algorithm}
\end{minipage}

\subsubsection{Cope with Multiple Shuffle Dependencies}
{\color{black}
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
}
% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
% For those pending shuffles, it is impossible to predict their sizes. 
% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
% But doing this introduces large overhead such as extra task serialization. 
% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
After scheduling, if the new $assigned\_id$ of a reduce task is not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

@@

>>>>

To solve this problem, we propose a new methodology named \textit{weighted reservoir sampling}.
SCache uses this method instead of the linear regression to predict output when using a RangePartitioner or a customized non-hash partitioner.
% we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
% Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable \reedited{parameter}. 
After that, the map function is called locally to process the sampled data. 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
The $inputSize_j$ is the input size of $j$th map task. 
% Note that sampling does not consume the input data of map tasks. 
% The $BlockSize_{ji}$ can be calculated by:
$BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}

\reedited{It can be discovered that as the increase of parameter $s$, more samples are included in the sampling, that is, the result of sampling is more accurate.
Based on our experiment, we discover that when $s$ is set to $3$, the result of sampling prediction is the best and much better than linear regression, as shown in Figure \ref{fig:range_pre_sample}.}
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide a much more accurate result than the linear regression. 
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}

@@

@@

\begin{minipage}{0.95\columnwidth}
	\begin{algorithm}[H]
	\caption{Heuristic MinHeap Scheduling for Single Shuffle}
	\label{hminheap}
		\begin{algorithmic}[1]
		\small
		\Procedure{schedule}{$m, host\_ids, p\_reduces$}
			\State $m\gets$ partition number of map tasks
			\State $R\gets$ sort $p\_reduces$ by size in \edited{decreasing} order
			\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
			\State $idx\gets 0$
			\While{$idx <$ len$R$}
			% \Comment{Schedule reduces by MinHeap}
			\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
			\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
			\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
			\State Sift down $M\left[0\right]$ by $size$
			\State $idx\gets idx+1$
			\EndWhile
			\State $max\gets$ maximum size in $M$
			% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
			\ForAll{$reduce$ in $R$}
			\Comment{Heuristic locality swap}
				\If{$reduce.assigned\_id \neq reduce.host\_id$}
					\State $p\gets reduce.prob$
					\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
					\State $upper\_bound \gets \left(1 + norm\right) \times max$
					\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
				\EndIf
			\EndFor
			\State
			\reedited{\Return $M$}
		\EndProcedure
		\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
			\State Swap tasks between node $host\_id$ and node $assigned\_id$
			\State of $reduce$ without exceeding the $upper\_bound$
			\State of both nodes.
			\State
			\reedited{\Return}
		\EndProcedure
		\end{algorithmic}
	\end{algorithm}
	\end{minipage}

\subsubsection{Cope with Multiple Shuffle Dependencies}
{\color{black}
A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
}

% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
% For those pending shuffles, it is impossible to predict their sizes. 
% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
% But doing this introduces large overhead such as extra task serialization. 
% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
After scheduling, if the new $assigned\_id$ of a reduce task is not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

@@

\begin{minipage}{0.95\columnwidth}
	\begin{algorithm}[H]
	\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
	\label{mhminheap}
		\begin{algorithmic}[1]
		\small
		\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\textit{shuffles}}$}
			\State $m\gets$ partition number of map tasks
			\Comment \textit{shuffles} are the previous schedule result 
			\ForAll{$r$ in $p\_reduces$}
				\State $r.size \mathrel{+}= \text{\textit{shuffles}}\left[r.rid\right].size$
				\State $new\_prob\gets \text{\textit{shuffles}}\left[r.rid\right].size / r.size$
				\If{$new\_prob\geq r.prob$}
					\State $r.prob\gets new\_prob$
					\State $r.host\_id\gets \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$
				\EndIf
			\EndFor
			\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
			\ForAll{\reedited{$host$} in $M$}
				\Comment Re-shuffle
				\ForAll{$r$ in $M\left[\reedited{host}\right].reduces$}
					\If{$host\neq \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$}
					\State Re-shuffle data to $host$
					\State $\text{\textit{shuffles}}\left[r.rid\right].assigned\_host\gets host$
					\EndIf
				\EndFor
			\EndFor
			\State
			\reedited{\Return $M$}
		\EndProcedure
		\end{algorithmic}
	\end{algorithm}
\end{minipage}
